Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-12-21 article/application_note.tex
add files for resubmission

\begin{abstract} 
iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer device repair-related questions. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract} % 174 words

@@

Founded in 2003, iFixit teaches thousands of users around the globe how to fix their own broken devices. This company provides over 40,000 free online repair guides and hosts a CQA, the \textit{Answers} forum, featuring questions pertaining to over 11,000 devices with over 130,000 user-posted solutions. One critical key feature of CQAs like \textit{Answers} is question response times. Fast response times have been shown to be associated with positive user experience and increased web traffic---factors that are extremely valuable to the reputation and longevity of the CQA \cite{Rechavi2011}. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask questions to minimize response times and for how forum design can be improved.

@@

\subsection{Related Work}

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered. However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \cite{Blumenstock2008} also determined that textual features (e.g. word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \cite{Fu2015} instead found non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality. A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate a question is of high quality also lead to faster response times.

\section{Materials}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download). Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received. Variables derived can be found in Table 1. The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table 5.

\section{Methods}

@@

\section{Results}

% Distribution of answer times
% \begin{figure}[!htbp]
%   \includegraphics[scale=0.5]{FIG1.pdf}
%   \label{fig:1}
% \end{figure}
% 
% % Kaplan-Meier curve
% \begin{figure}[!htbp]
%   \includegraphics[scale=0.5]{FIG2.eps}
%   \label{fig:2}
% \end{figure}

@@

\section{Discussion}

>>>>

\begin{abstract} 
iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer device repair-related questions. As the time until a question receives its first response is an important aspect of CQAs and, at present, has not been thoroughly investigated, this paper presents a survival analysis of response times of questions posted on iFixit's \textit{Answers} forum. A Cox proportional hazards model was developed to identify signficanlty associated variables. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract} % 174 words

@@

Founded in 2003, iFixit teaches thousands of users how to fix their own broken devices. This company provides over 40,000 free online repair guides and hosts a CQA, the \textit{Answers} forum, featuring questions pertaining to over 11,000 devices with over 130,000 user-posted solutions. One critical key feature of CQAs like \textit{Answers} is question response times. Fast response times have been shown to be associated with positive user experience and increased web traffic---factors that are extremely valuable to the reputation and longevity of the CQA \cite{Rechavi2011}. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask questions to minimize response times and for how forum design can be improved.

@@

\subsection{Relevant Data}

The data analyzed contains 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download). Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received. Variables derived can be found in Table 1. The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table 5.

\section{Methodology}

@@

\section{Application of Methodology}

@@

\section{Conclusion and Discussion}
